A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-05-03 report_clean/numerics.tex
intro looks a bit more reasonable now

\subsection{Frequency Domain Problem}
\label{sec:freq_dep}
\subsubsection{Validity of the Implementation}
To check the validity of the code, we first perform a numerical experiment with (formally chosen) parameters:
\begin{align}
\label{eq:parameters}
\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}, \qquad \mrev{\nu=0, \qquad \theta=0.}
\end{align}
\urev{It can be shown that $E_{y}$ that solves (\ref{eq:main_frequency_domain}) with the above parameters,  
and $\nu=0$, satisfies the Airy equation, see also Remark \ref{remark:other},
\begin{align*}
 E_y''-xE_y=0,\qquad x\in [-L,\; H].
\end{align*}
One of the solutions of this equation, an Airy function $\Ai(x)$, see \cite[Chapter 10.4]{abramowitz_stegun}, is analytic and 
decays rapidly as $x\rightarrow \infty$. }
\mrev{Hence, choosing $H$ sufficiently large (the actual value used in the experiments $H=10$, where $\Ai'(10)\approx -3.5e-10$) and the boundary conditions as 
\begin{align}
\label{eq:bcs_airy}
\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2i\Ai(-L)+\Ai'(-L),\qquad 
\partial_{1}E_{y}(H)=0\approx \Ai'(H),
\end{align}
where $\Ai(x)$ is an Airy function, we ensure that $E_{y}$ that solves the above problem is well approximated by $\Ai(x)$, and $E_{x}$ by $-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$. 
The well-posedness of the respective variational formulation for $\nu=0$ is due to Remark \ref{remark:other}. }

>>>>

\subsection{Frequency Domain Problem}
\label{sec:freq_dep}
\subsubsection{Validity of the Implementation}
To check the validity of the code, we first perform a numerical experiment with (formally chosen) parameters:
\begin{align}
\label{eq:parameters}
\alpha(x)=x^2+1,\qquad \delta(x)=\left(\alpha^2+x\alpha\right)^{\frac{1}{2}}, \qquad \mrev{\nu=0, \qquad \theta=0.}
\end{align}
\urev{It can be shown that $E_{y}$ that solves (\ref{eq:main_frequency_domain}) with the above parameters,  
and $\nu=0$, satisfies the Airy equation, see also Remark \ref{remark:other},
\begin{align*}
 E_y''-xE_y=0,\qquad x\in [-L,\; H].
\end{align*}
One of the solutions of this equation, an Airy function $\Ai(x)$, see \cite[Chapter 10.4]{abramowitz_stegun}, is analytic and 
decays rapidly as $x\rightarrow \infty$. }
\mrev{Hence, choosing $H$ sufficiently large (the actual value used in the experiments $H=10$, where $\left|\Ai'(10)\right|<1e-9$) and the boundary conditions as 
\begin{align}
\label{eq:bcs_airy}
\partial_{1}E_{y}(-L)+2iE_{y}(-L)=2i\Ai(-L)+\Ai'(-L),\qquad 
\partial_{1}E_{y}(H)=0\approx \Ai'(H),
\end{align}
where $\Ai(x)$ is an Airy function, we ensure that $E_{y}$ that solves the above problem is well approximated by $\Ai(x)$, and $E_{x}$ by $-i\frac{\delta(x)}{\alpha(x)}\Ai(x)$. 
The well-posedness of the respective variational formulation for $\nu=0$ is due to Remark \ref{remark:other}. }
